The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-03 paper/ms.tex
98 Tau updates

>>>>

\begin{figure*}
\plotone{98_Tau_pub.pdf}
\caption{Summary plots for \textsc{k2sc}-corrected final halo light curve for the eclipsing binary 98~Tauri, in a similar format to Figure~\ref{fig:rholeo}. The residuals to the position and time GP are not shown, as the time GP fits poorly to the deep eclipse. The polynomial trend and Lomb-Scargle periodograms are conditioned on the out-of-transit points only.}
\label{fig:98tau}
\end{figure*}
